---
title: "R Notebook"
output: html_notebook
---

The code here cross validates a model given a data set named dat12_14 with a two factor outcome variable called loan_status and a grid of parameters for tuning. It takes as input a grid of parameters for the `ranger` package in R. The `ranger` package builds random forest models and takes the parameters `mtry` and `numt` where `mtry` sets the number of variables to include in each regression and `numt` sets the number of trees to include in each forest.    

```{r}
library(ranger)
```

```{r}
dat12_14 <- read.csv("C:/Users/yalep/Desktop/R Sandbox/dat12_14a.csv") 
dat12_14$loan_status <- as.factor(dat12_14$loan_status)
```

```{r}
dplyr::glimpse(dat12_14)
```

```{r}
visdat::vis_miss(dat12_14)
```

```{r}
# Size of subsets and sequence for subsetting       

CV <- 10
test_l <- nrow(dat12_14)%/%CV
seq <- seq(from=0, to=10*test_l, by = test_l)
```

```{r}

mtry <- c(3, 4)
numt <- c(300, 200)

mean_kappa <- c()
mean_AUC <- c()
mean_Acc <- c()

output <- list()

for(j in 1:length(mtry)){

test <- list()
train <- list()
pred_cv <- list()
results <- list()
metrics <- list()
kappa <- c()
Acc <- c()
AUC <- c()

output$mtry[j] <- mtry[j]
output$numt[j] <- numt[j]

for(i in 1:CV){
  test_rows <- seq[i]:seq[i+1]
  test[[i]] <- dat12_14[test_rows,]
  train[[i]] <- dat12_14[-test_rows,]
  ranger_lending_cv <- ranger(loan_status ~ ., data = train[[i]], 
                             num.threads = 3, mtry = mtry[j], num.trees = numt[j])
  pred_cv[[i]] <- predict(ranger_lending_cv, data = test[[i]])$predictions

  results[[i]] <- bind_cols(truth = test[[i]]$loan_status, 
                 estimate=(as.numeric(pred_cv[[i]])-2)^2, 
                 f_estimate = pred_cv[[i]])
  
  metrics[[i]] <- results[[i]] %>% 
    metrics(truth = truth, estimate = f_estimate)
  kappa[i] <- metrics[[i]]$.estimate[2] 
  Acc[i] <- metrics[[i]]$.estimate[1]
  
  auc <- results[[i]] %>%
    roc_auc(truth = truth, estimate)
  AUC[i] <- auc$.estimate
}
  mean_kappa[j] <- mean(kappa)
  mean_AUC[j] <- mean(AUC)
  mean_Acc[j] <- mean(Acc)
}  
output$mean_Acc <- mean_Acc
output$mean_AUC <- mean_AUC
output$mean_kappa <- mean_kappa
```

```{r}
output
```
























