---
title: "R Notebook"
output: html_notebook
---

The code here cross validates a model given a data set named dat12_14 with a two factor outcome variable called 
loan_status and a grid of parameters for tuning. It takes as input a grid of parameters for the `ranger` package 
in R. The `ranger` package builds random forest models and takes the parameters `mtry` and `numt` where `mtry` sets
the number of variables to include in each regression and `numt` sets the number of trees to include in each forest.

It outputs a list called `output` containing the supplied pairs of input parameters and the crossvalidation results
for each. The results of the crossvalidation are the mean Accuracy, AUC, Cohen's \(\kappa\) for all of the runs of 
the crossvalidation.    


```{r}
library(ranger)
```

Read in the data from github user ypaulsen. 

```{r}
dat12_14 <- read.csv("https://github.com/ypaulsen/Cross-Validation-in-R/raw/main/dat12_14a.csv") 
dat12_14$loan_status <- as.factor(dat12_14$loan_status)
```

First lets have a look at the data: 

```{r}
dplyr::glimpse(dat12_14)
```

No missing values: 

```{r}
visdat::vis_miss(dat12_14)
```

This chunk starts the crossvalidation by setting up the number of subsets to use and generating the sequence of index
numbers to split the dataset during the nested for loop in the next code chunk.  

```{r}
# Size of subsets and sequence for subsetting       

CV <- 10
test_l <- nrow(dat12_14)%/%CV
seq <- seq(from=0, to=10*test_l, by = test_l)
```

This code contains a nested for-loop that achieves a crossvalidation in the i loop where i is the number of subsets
to divide the dataset into for crossvalidation; and it repeats that procedure in the j-loop where j is the number of
pairs of parameters in the grid of test parameters assigned in the first two lines of the code chunk.  


```{r}

mtry <- c(3, 4)
numt <- c(300, 200)

mean_kappa <- c()
mean_AUC <- c()
mean_Acc <- c()

output <- list()

for(j in 1:length(mtry)){

test <- list()
train <- list()
pred_cv <- list()
results <- list()
metrics <- list()
kappa <- c()
Acc <- c()
AUC <- c()

output$mtry[j] <- mtry[j]
output$numt[j] <- numt[j]

for(i in 1:CV){
  test_rows <- seq[i]:seq[i+1]
  test[[i]] <- dat12_14[test_rows,]
  train[[i]] <- dat12_14[-test_rows,]
  ranger_lending_cv <- ranger(loan_status ~ ., data = train[[i]], 
                             num.threads = 3, mtry = mtry[j], num.trees = numt[j])
  pred_cv[[i]] <- predict(ranger_lending_cv, data = test[[i]])$predictions

  results[[i]] <- bind_cols(truth = test[[i]]$loan_status, 
                 estimate=(as.numeric(pred_cv[[i]])-2)^2, 
                 f_estimate = pred_cv[[i]])
  
  metrics[[i]] <- results[[i]] %>% 
    metrics(truth = truth, estimate = f_estimate)
  kappa[i] <- metrics[[i]]$.estimate[2] 
  Acc[i] <- metrics[[i]]$.estimate[1]
  
  auc <- results[[i]] %>%
    roc_auc(truth = truth, estimate)
  AUC[i] <- auc$.estimate
}
  mean_kappa[j] <- mean(kappa)
  mean_AUC[j] <- mean(AUC)
  mean_Acc[j] <- mean(Acc)
}  
output$mean_Acc <- mean_Acc
output$mean_AUC <- mean_AUC
output$mean_kappa <- mean_kappa
```

```{r}
output
```
























